---
title: "Look Whose Interrupting"
subtitle: "Racialized and Gendered Judgments in Interruptive Contexts"
author: "Dean Manko, Judith Degen, Katherine Hilton, Brandon Waldon"
date: "Spring 2022"
urlcolor: blue
output:
  bookdown::pdf_book:
    toc: true
    fig_caption: yes
    includes:
      in_header: plot_formatting.tex
    toc_depth: 4
    highlight: tango

bibliography: [references/references.bib]
biblio-style: apalike
nocite: '@*'
---
```{r setup, echo = FALSE, message = FALSE}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("dplyr")
library("pwr")
library("lme4")
library("lmerTest")
library("ggplot2")
library("bootstrap")
library("tm")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# include references for used packages
write_bib(.packages(), "references/packages.bib") 

#set the default ggplot theme
theme_set(theme_classic())
```



Body of thesis goes here — *whoa*.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

